{{< var titll >}}

### 2024-07-08 index.qmd
abc

---
title: "{{< var titll >}}"
output: github_document
execute: 
  cache: false
webr:
  show-startup-message: true      # Display status of webR initialization
  show-header-message: false      # Check to see if COOP&COEP headers are set for speed.
  packages: ['dplyr','data.table','readr']             # Pre-install dependencies
  cell-options:
    autorun: true
filters:
  - panelize
  - webr
---

@@

# Testing
## ABC
Write some text here
```{web-r}
```

abc

## Installling packages
```{webr-r}
webr::install("ManifoldDestinyWASMD", repos = "https://lotariohw26.github.io/MD_WASMC")
webr::install("ManifoldDestinyWASMP", repos = "https://lotariohw26.github.io/MD_WASMC")
dplyr::select(ManifoldDestinyWASMD::abc,S,T,U,V)
# readr::read.csv("/tmp/RtmpHKcMHo/d5ace5deaed228c73ccaf4fb/0.csv")
```

## Loading  data
```{webr-r}
dplyr::select(ManifoldDestinyWASMD::abc,S,T,U,V)
```

>>>>

---
title: "{{< var titll >}}"
output: github_document
execute: 
  cache: false
webr:
  show-startup-message: true      # Display status of webR initialization
  show-header-message: false      # Check to see if COOP&COEP headers are set for speed.
  packages: ['dplyr','data.table','readr','ggplotly']             # Pre-install dependencies
  cell-options:
    autorun: true
filters:
  - panelize
  - webr
---

@@

# Testing (latest from Ed's Youtube stream)

## Installling packages

```{webr-r}
webr::install("ManifoldDestinyWASMD", repos = "https://lotariohw26.github.io/MD_WASMC")
webr::install("ManifoldDestinyWASMP", repos = "https://lotariohw26.github.io/MD_WASMC")
df <- ManifoldDestinyWASMD::yout
dplyr::select(df[[1]],S,T,U,V)
```

[Nevada](https://docs.google.com/spreadsheets/d/1gCfmuK44sUeb0Hb0plAc8VllPSjtUiEHWlJjeHq3xXY/edit?gid=0#gid=0)

```{webr-r}
library(plotly)                                                                                          
# Create sample data                                                                                     
x <- seq(-5, 5, length.out = 100)                                                                        
y <- x                                                                                                   
z <- outer(x, y, function(x, y) cos(sqrt(x^2 + y^2)))

# Create 3D scatter plot                                                                                 
plot_ly(x = x, y = y, z = z, type = "scatter3d", mode = "markers")                                       
```

```{webr-r}
library(ggplot2)

# Create a sample data frame                                                                             
data <- data.frame(                                                                                      
  x = c(1, 2, 3, 4, 5),                                                                                  
  y = c(2, 3, 5, 7, 6)                                                                                   
)

# Create a scatter plot using ggplot2                                                                    
ggplot(data, aes(x = x, y = y)) +                                                                        
  geom_point()                                                                                           
```

### 2024-07-08 presentation.qmd
abc

@@

>>>>

![](images/ss.png){width=300}

> abstract: on august 15th, **2004**, venezuelans had the opportunity to vote
in a presidential recall referendum **to decide whether or not president hugo
chávez should be removed from office.** **the process was largely computer-
ized using a touch-screen system.** in general the ballots were not manually
counted. the significance of the high linear correlation (0.99) between the
number of requesting signatures for the recall petition and the number of op-
position votes in computerized centers is analyzed. The same-day audit was
found to be not only ineffective but a source of suspicion...

{{< video https://www.youtube.com/watch?v=YQg1Cr3vRic&t=76s >}}

![](images/manifold.png){width=300}

@@

- Condition on that $R^2$ falls within the critical region.
  - Normal form
```{r, echo=F, out.width="40%", fig.cap=""}
pr2n <- paste0(rprojroot::find_rstudio_root_file(),'/images/r2n.png')
knitr::include_graphics(c(pr2n))
```

 - Hybrid form
```{r, echo=F, out.width="40%", fig.cap=""}
pr2h <- paste0(rprojroot::find_rstudio_root_file(),'/images/r2h.png')
knitr::include_graphics(c(pr2h))
```
